\begin{thebibliography}{1}

\bibitem{ref:ping_pong_robot} K. Muelling, J. Kober and J. Peters. Simulating Human Table Tennis with a Biomimetic Robot Setup, From \emph{Animals to Animats 11, International Conference on the Simulation of Adaptive Behavior (SAB)}, 2010.

\bibitem {ref:pool_robot} T. Martin, K. H. L. Ho and J. Baldwin. Snooker Robot Player - 20 Years
on. From \emph{Computational Intelligence and Games, 2007. CIG 2007. IEEE Symposium on}, 2007.

\bibitem{ref:Georgia_foosball_table} M. Aeberhard, S. Connelly, E. Tarr and N. Walker. Single Player Foosball Table with an Autonomous Opponent, 2007.

\bibitem {ref:Uakron_foosball_table} A. Alsalihi, K. Najjar, B. V. Scoy and J. Zifer. Automated Foosball Table, 2011.

\bibitem {ref:KiRo} T. Weigel. KiRo - A Table Soccer Robot Ready for the Market. From \emph{Robotics and Automation, 2005. ICRA 2005. Proceedings of the 2005 IEEE International Conference on}, 2005.

\bibitem {ref:Eindhoven_foosball_table} R. Janssen. The design of a semi-automated football table. From \emph{Control Applications (CCA), 2010 IEEE International Conference on}, 2010.

\bibitem{ref:cologn_foosball_table} Allied Vision Technologies and University of Applied Sciences, Cologne. Automatic Foosball Robot, 2007. \url{http://www.alliedvisiontec.com/uploads/media/AVT-Case-Study-Kickroboter_EN.pdf}.


\bibitem{ref:DTU_foosball_table} A. C. Myrup and M. Ø. Thomsen. Software til automatiseret bordfodbold, 2007. \url{http://foospmp.myl.dk/media/rapport.pdf}.

\bibitem{ref:Machine_Learning} D. Zhang and B. Nebel. Learning a Table Soccer Robot a New Action Sequence
by Observing and Imitating, 2007.

\bibitem{ref:Decision_Theoretic} M. Tacke, T. Weigel and B. Nebel. Decision-Theoretic Planning for Playing
Table Soccer, 2004.

\bibitem{ref:StarKick} \url{http://www.merkur-starkick.de/en/default.htm} last visited 29-05-2014.

\bibitem{ref:StarKick_1_0}  T. B. Jørgensen and J. P. Buch. StarKick - Det automatiserede fodboldbord, 2012.

\bibitem{ref:Motors} FAULHABER. DC-Micromotors Series 3863C Technical datasheet, Aug. 2009.

\bibitem{ref:Camera} Point Grey. Firefly MV datasheet, Apr. 2011.

\bibitem{ref:Motor_Encoder} FAULHABER. Series IE2- 1024 Magnetic Encoders Technical datasheet, 2012-2013 edition.

\bibitem{ref:Motor_drivers} FAULHABER. Series MCDC 2805 Motion controller for DC-Micromotors Instruction Manual, June 2001.

\bibitem{ref:Teensy} PRJC. Teensy 3.1 \url{https://www.pjrc.com/teensy/teensy31.html} last visited 30/05-2014.

\bibitem{ref:Teensyduino} PRJC. Teensyduino \url{https://www.pjrc.com/teensy/teensyduino.html} last visited 30/05-2014.

\bibitem{ref:Teensy_mic} Freescale Semiconductor. K20 Sub-Family Technical datasheet, rev. 3  Nov. 2012.

\bibitem{ref:Tiva} Texas Instruments. Tiva\texttrademark C Series TM4C123G LaunchPad Evaluation Board User's Guide, Apr. 2013.

\bibitem{ref:Tiva_mic} Texas Instruments. Tiva™ TM4C123GH6PM Microcontroller Data Sheet, Mar. 2014.

\bibitem{ref:uvision} ARM. Keil uvision IDE \url{http://www.keil.com/uvision/}, last visited 30/05-2014.

\bibitem{ref:FreeRTOS} FreeRTOS. \url{http://www.freertos.org/}, last visited 30/05-2014.

\bibitem{ref:PWM_strategy} D. Y. Ohm and R. J. Oleksuk. Influence of PWM Schemes and Commutation Methods for DC and Brushless Motors and Drives, 2002.

\bibitem{ref:Baud_rate} Paroscientific, Inc. Typical Maximum Cable Drive Distances for Digiquartz\textregistered Transducers and Intelligent Transmitters, 2001. 

\bibitem{ref:DSP} L. Tan. Digital Signal Processing Fundamentals and Application, 2008.

\bibitem{ref:Modern Control Systems} Richard C. Dorf and Robert H. Bishop. Modern Control Systems 12th edition, 2011.

\bibitem{ref:Self-tuning} Bobál, Böhm, Fessl and Machá\v{c}ek. Digital Self-tuning Controllers. 2005.

\bibitem{ref:nonlinearities} Gang Tao and Petar V. Kokotovi\'{c}. Adaptive Control of Systems with Actuator and Sensor Nonlinearities. 1996

\bibitem{ref:Power ele} Mohan, Underland and Robbins, Power Electronics: Converters applications, and Design. 2002.

\bibitem{ref:ident} Lennart Ljung. 
\newblock{System Identification Toolbox\texttrademark: User's Guide.} 2014.

\bibitem{ref:ROS} Opens Source Robotics Foundation \url{http://www.ros.org/} last visited 01/6-2014.

\bibitem{ref:h_bridge}ST microelectronics,"DMOS Full Bridge Driver",L6203 Datasheet.Jul 1997

\end{thebibliography} 

\newpage